---
author: "Stefan Küthe"
title: "Introduction to openlayers for R"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{openlayers}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
library(openlayers)
knitr::opts_chunk$set(
  eval = FALSE,
  message = FALSE
)
```

Openlayers for R makes the open-source JavaScript library [OpenLayers](https://openlayers.org) available within R via the [htmlwidgets](http://www.htmlwidgets.org) package. So it is fun to create interactive maps and use them in Shiny apps or RMarkdown documents.

## The map widget

Basically you create a map widget and add tiles, features, controls and interactions to it.

```{r}
# Create a default map widget
map <- ol()

# Pass some options
map <- ol(options = ol_options(max_zoom = 16))
```

## Basic tiles

```{r, eval=FALSE}
# OSM
ol() %>% add_osm_tiles()

# Stamen
ol() %>% add_stamen_tiles("watercolor")

# Custom provider
provider <- "http://cartodb-basemaps-{a-c}.global.ssl.fastly.net/dark_all/{z}/{x}/{y}.png"

ol() %>% add_xyz_tiles(provider, attribution = "Add attribution here ...")

# Combining tiles
ol() %>%
  add_stamen_tiles() %>%
  add_stamen_tiles("terrain-labels",
                   options = layer_options(max_resolution = 13000))
```

## WMS tiles

```{r, eval=FALSE}
ol() %>%
  add_stamen_tiles() %>%
  add_wms_tiles("http://ows.terrestris.de/osm/service",
                layers = "TOPO-WMS",
                attribution = "Do not forget to insert the attribution!",
                options = layer_options(opacity = 0.5))
```

## Vector tiles

```{r}
# Mapbox example

token <- "your_access_token"
mapbox <- paste0("https://{a-d}.tiles.mapbox.com/v4/",
                 "mapbox.mapbox-streets-v7/",
                 "{z}/{x}/{y}.vector.pbf",
                 "?access_token=", token)

ol() %>% add_vector_tiles(mapbox, mapbox_attribution())
```

## Features

```{r, eval=FALSE}
require("geojsonio")
require("sf")

# Points
point_features <- us_cities[1:5, ]

ol() %>% add_stamen_tiles() %>%
  add_features(point_features)

# Lines
line_feature <- point_features[, c("long", "lat")] %>%
  as.matrix() %>% st_linestring()

ol() %>% add_osm_tiles() %>%
  add_features(point_features) %>%
  add_features(line_feature)

# Polygons
nc <- st_read(system.file("gpkg/nc.gpkg", package = "sf"),
              quiet = TRUE)

ol() %>% add_osm_tiles() %>%
  add_features(nc)
```

## Controls

```{r, eval=FALSE}
# Overview map
ol() %>% add_osm_tiles() %>%
  add_overview_map(collapsed = FALSE)

## ... ##
```

## Interactions

...
